Choosing climate forcing for numerical simulations of the Cordilleran ice sheet

### 2013-02-14 sections/model.tex
Initial commit
Created an embryonic paper draft with abstract, sections and figures.
Added techincal note for Constantine

% ----------------------------------------------------------------------
\introduction
\label{sec:intro}
% ----------------------------------------------------------------------

\begin{figure}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=8cm]{cordillera-climate-locmap}
	\end{center}
	\caption{Shaded relief map of northern North America. The frame delimits the modelling domain. After ETOPO1 \citep{data:etopo1} and Natural Earth Data \citep{data:naturalearth}.}
	\label{fig:locmap}
\end{figure}

>>>>

% ----------------------------------------------------------------------
\section{Model setup}
\label{sec:setup}
% ----------------------------------------------------------------------

\begin{figure}\begin{framed}
	\textbf{Technical note for Constantine}
	\todo{Remove this note}

	All my simulations use the same set of options except of a different \verb|-atmosphere_given_file| (climate forcing) and \verb|-atmosphere_delta_T_file| (temperature offset). Here comes the options that I used; I think you saw them a couple of times now. I simplified paths and filenames and remove output options for readability

	\begin{verbatim}
	mpprun pismr -boot_file boot.nc -Mx 150 -My 300
	-Mz 51 -Lz 5000 -Mbz 11 -Lbz 1000 -ys 0 -ye 10000
	-topg_to_phi 10,30,0.0,200.0
	-atmosphere given,lapse_rate,delta_T -atmosphere_given_file atm.nc
	-atmosphere_given_period 1
	-temp_lapse_rate 6 -atmosphere_lapse_rate_file atm.nc
	-atmosphere_delta_T_file step-cool08.nc
	-surface pdd -pdd_annualize
	-ocean constant,delta_SL -ocean_delta_SL_file step-low120.nc
	-ssa_sliding
	-config_override config.nc
	\end{verbatim}

	And here comes the relevant contents of \verb|config.nc|:

	\begin{verbatim}
	netcdf config \{
	variables:
	  byte pism_overrides ;
	    pism_overrides:bed_deformation_model = "lc" ;
	    pism_overrides:do_thickness_calving = "true" ;
	    pism_overrides:calving_at_thickness = 200. ;
	    pism_overrides:calving_front_stress_boundary_condition = "yes" ;
	    pism_overrides:part_grid = "yes" ;
	    pism_overrides:part_redist = "yes" ;
	    pism_overrides:kill_icebergs = "yes" ;
	    pism_overrides:bootstrapping_geothermal_flux_value_no_var = 0.07 ;
	    pism_overrides:pdd_factor_snow = 0.003 ;
	    pism_overrides:pdd_factor_ice = 0.008 ;
	    pism_overrides:pdd_refreeze = 0.6 ;
	    pism_overrides:pdd_std_dev = 5 ;
	\}

	\end{verbatim}

\end{framed}\end{figure}
